Type Error Telemetry at Scale

### 2023-09-30 programming23/paper.tex
cleanup

In \cref{f:error-changes}, however, nearly \pct{3} of \mstrict{}-mode records
increase the number of \mstrict{} errors without increasing \FS{} errors.
Further inspection reveals that the situation is a bit worse, as
some records increase \mstrict{} errors without changing the \FS{} errors:
\begin{itemize}
  \item
    \pct{22} of \mstrict{} records increase (\addsym{}) the number of type errors
    but maintain (\keepsym{}) the number of \FS{} errors.
\end{itemize}
The reason for the discrepancy is that \mstrict{} mode and \FS{} analysis
assign different types to the data model: \mstrict{} assigns a top type
and requires downcasts at use sites, whereas \FS{} analysis uses the
dynamic gradual type.
Dealing with these data model errors may be a source of frustration
for creators using \mstrict{} mode.

>>>>

In \cref{f:error-changes}, however, nearly \pct{3} of \mstrict{}-mode records
increase the number of \mstrict{} errors without increasing \FS{} errors.
Further inspection reveals that the situation is a bit worse, as
some records increase \mstrict{} errors without changing the \FS{} errors:
    \pct{22} of \mstrict{} records increase (\addsym{}) the number of type errors
    but maintain (\keepsym{}) the number of \FS{} errors.

The reason for the discrepancy is that \mstrict{} mode and \FS{} analysis
assign different types to the data model: \mstrict{} assigns a top type
and requires downcasts at use sites, whereas \FS{} analysis uses the
dynamic gradual type.
Dealing with these data model errors may be a source of frustration
for creators using \mstrict{} mode.
